---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vppv

<!-- badges: start -->
<!-- badges: end -->

The goal of vppv is to calculate the VPPV: The Ventilation induced Pulse Pressure Variation. This is a hemodynamic parameter that is the percentual change in Bloodpressure (Pulse Pressure) induced by mechanical ventilation. This specific method is especially fit to quantify this effect in patients with atrial fibrillation. For more details see: 'New algorithm to quantify cardiopulmanary interaction in patients with atrial fibrillation: a proof-of-concept study.' [BJA 2021; 126(1): 111-119](https://doi.org/10.1016/j.bja.2020.09.039)

## Installation

You can install the development version of vppv from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pwyffels/vppv")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(vppv)
## basic example code

# selecting the right date.frame format
dat = VPPV_frame(afib, time, RR0,RR1, PP,12)

# building the model
model_gam <- VPPV_gam(dat)

# extracting the VPPV value
VPPV_value(model_gam)

```

